|

### 2024-08-22 reproducibility/manuscript/manuscript.qmd
docs(manuscript): use v2 cached figures
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

::: {#fig-model-results}
![](figures/fig.pdf)

@@

::: {#fig-lineage-tracing}
![](figures/fig.pdf)

@@

::: {#extfig-model-results}
![](figures/fig.pdf)

@@

::: {#extfig-model-2-result}
![](figures/fig.pdf)

@@

::: {#extfig-lineage-tracing}
![](figures/fig.pdf)

@@

::: {#extfig-lineage-tracing-2}
![](figures/fig.pdf)

>>>>

::: {#fig-model-results}
![](figures/v2/Figure2.png)

@@

::: {#fig-lineage-tracing}
![](figures/v2/Figure3.png)

@@

::: {#extfig-model-results}
![](figures/v2/Supplementary-Figure2.png)

@@

::: {#extfig-model-2-result}
![](figures/v2/Supplementary-Figure3.png)

@@

::: {#extfig-lineage-tracing}
![](figures/v2/Supplementary-Figure4.png)

@@

::: {#extfig-lineage-tracing-2}
![](figures/v2/Supplementary-Figure5.png)
